On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-02-20 v-research_experiment-alpha.tex
make git happy

\begin{definition}{\bf Hacking Process}\label{def:hackingprocess}
An \emph{Attack} is the act of making operational an \emph{Exploitation Process} 
	causing an Incident. \fix{mr}{Threat? Asset?}
\end{definition}

@@

The formalization of the Exploitation and Hacking processes is the
formalization of two foundational cybersecurity concepts which lay the basis
for the definition (and formalization) of the cybersecurity theory in the next
Section (Section~\ref{sec:theory}). However, the formal definition of those
processes shall (i) correlate the formal definition of agents (i.e. the
Definition~\ref{def:agent}) with the Causality principle (i.e. the
formalization of the Kripke structure in Definition~\ref{def:causality}), and,
most importantly, (ii) formally define a system as a structure of agents. For
the sake of clarity, we then postpone the formalization of the two processes to
the next Section.

>>>>

\begin{definition}{\bf Hacking Process}\label{def:hackingprocess}
An \emph{Attack} is the act of making operational an \emph{Exploitation Process} 
	causing an Incident. 
\end{definition}

@@

The formalization of the Exploitation and Hacking processes is the
formalization of two foundational cybersecurity concepts which lay the basis
for the definition (and formalization) of the cybersecurity theory in the next
Section (Section~\ref{sec:theory}). However, the formal definition of those
processes shall (i) correlate the formal definition of agents (i.e. the
Definition~\ref{def:agent}) with the Causality principle (i.e. the
formalization of the Kripke structure in Definition~\ref{def:modallogic}), and,
most importantly, (ii) formally define a system as a structure of agents. For
the sake of clarity, we then postpone the formalization of the two processes to
the next Section.
